Interpretable Neural Networks using EAGGA

### 2025-03-12 paper/main.tex
first bullets on MOO a posteriori

\begin{keywords}
  tabular data, multi-objective optimization, deep learning
\end{keywords}

@@

\subsection{Multi-Objective Optimization}
- problem: all aforementioned approaches are a-priori approaches -> we choose best HPs (weight decay, features used, dropout) w.r.t. performance
- intro MOO
\subsubsection{Pareto-optimality}
\subsubsection{A-priori}
\subsubsection{A-posteriori}
- NSGA-II (MOEA)
  * non-dominated sorting
  * crowding distance
  -> give intuition why non-dom-sort (asc) + crowding dist (desc) makes sense for selecting individuals

%likely shouldn't be an entire section
\section{EAGGA}
- for our problem (interpretability) we cannot use regular EA algorithms as we are also interested in reducing pairwise interactions + non-monotone feature effects
- this creates high-dim search space as shown in EAGGA paper -> they provide a framework to efficiently traverse through a space that is reduced to only sensible HP
  configuration (e.g. interaction of A,B with A monot incr and B monot decr -> couldn't be guaranteed -> don't look at it in first place)
- NSGA-II inspired evolutionary / genetic algorithm
- introduces group structure for more efficient optimization over the entire search space

>>>>

\begin{keywords}
  tabular data, multi-objective optimization, interpretability, deep learning
\end{keywords}

@@

\subsection{Multi-Objective Optimization}
- intro MOO
\subsubsection{Pareto-optimality}
\subsubsection{A-priori}
\subsubsection{A-posteriori}
- problem a priori
  * either restrict search space to ``enforce our will'' (e.g. only use 50\% of features), optimise only prediction performance + use this
  * or leave search space unrestricted but adjust loss function to incorporate multiple objectives + take optimum from there
  * in either case: no knowledge of interplay between HP config + performance on all objectives
  * a-posteriori evaluates configs just as a-priori, but keeps track of multiple ``best'' (non-dominated) solutions -> makes relationship between HP config + objectives visible
- NSGA-II (MOEA)
  * non-dominated sorting
  * crowding distance
  -> give intuition why non-dom-sort (asc) + crowding dist (desc) makes sense for selecting individuals

%likely shouldn't be an entire section
\section{EAGGA}
- combines all previously mentioned topics: interpretability, HPO, MOO
- for our problem (interpretability) we cannot use regular EA algorithms as we are also interested in reducing pairwise interactions + non-monotone feature effects
- this creates high-dim search space as shown in EAGGA paper -> they provide a framework to efficiently traverse through a space that is reduced to only sensible HP
  configuration (e.g. interaction of A,B with A monot incr and B monot decr -> couldn't be guaranteed -> don't look at it in first place)
- NSGA-II inspired evolutionary / genetic algorithm
- introduces group structure for more efficient optimization over the entire search space
